---
title: "Regular Expressions: Problem Set"
author: "YOUR NAME"
output: html_document
---


### 0. Preparation: Load packages

```{r, message = FALSE}
# enter your R code here
library(tidyverse) # example
library(rvest)
sum(1, 2
```


<br>

### 1. The ultimate regular expression

Find a regular expression that matches anything of any length! Prove that it works using several examples.


```{r, eval = TRUE}
# enter your R code here
```


<span style="color:blue">
If you want to add a comment outside the R code block, use this <span> block! (just copy the <span>...</span> lines for future comments in the Rmd file.)
</span>

<br>

### 2. Finding strings that are matched by regular expressions

Describe the types of strings that conform to the following regular expressions and construct an example that is matched by the regular expression.

a. [0-9]+\\$
b. b[a-z]{1,4}
c. .*?\\.txt$
d. \\d{2}/\\d{2}/\\d{4}
e. <(.+?)>.+?</\\1>

```{r}
# Example
str_extract_all("Phone 150$, TV 690$", "[0-9]+\\$") # Answer: this regex describes prices in dollars

# enter your R code here to solve b. to e.
```


<br>

### 3. Manipulating an email address

Consider the mail address  datalover89[at]aol[dot]com. Now, complete the following tasks.

a. Transform the string to a standard mail format (i.e., replace the square brackets with the appropriate symbols) using regular expressions.
b. Now extract the local-part ("datalover89") and the domain ("aol") separately. 

```{r}
# enter your R code here
```


<br>

### 4. A secret message
The following code hides a secret message. Crack it with R and regular expressions. Once you have cracked it, try to collapse the solution in one single string. <i>Hint: Some of the characters are more revealing than others!</i>

```{r}
secret <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.RqoE65fGEa1otfb7wXm24k.6t3sH9zqe5fy89n6Ed5t9kc4fR905gmc4Ogxo5nhk!gr"

# enter your R code here
```


