---
title: "A Primer to Web Scraping with R - Meeting 1 Notes"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---


```{r}
library(tidyverse)
library(rvest)
```


## Workshop logistics
---------------------------------

- Code and materials: https://github.com/hertie-data-science-lab/ds-workshop-webscraping
- Feedback form: https://docs.google.com/forms/d/e/1FAIpQLSdp9Z4IWAO1cyf3-MVwpCKN-Ydn0mwXzaQ9C0L5H67B7aBGOA/viewform?vc=0&c=0&w=1&flr=0&usp=mail_form_link
- Book? https://www.dropbox.com/s/7pooidefpwzp6wo/wiley-adcr-v2.pdf?dl=0
- Issues, questions
- Your experience with web technologies? And R?


## Today's agenda
---------------------------------

2-2.50pm: Scraping static webpages
3-3.50pm: Scraping dynamic webpages


## Static scraping case study: mapping breweries
---------------------------------

See 01-case-study-2-breweries.r


## Your questions on regex and static web scraping
---------------------------------

<br>

*SelectorGadget*

I tried to play a bit with the SelectorGadget and it worked pretty well. Could you let us know more about the 20-30% where you said it would most likely not work and how you would approach such a case? Do you have a real life example where we could see how you went about it?


```{r}
url <- "https://en.wikipedia.org/wiki/List_of_female_scientists_in_the_20th_century"
browseURL(url)
url_parsed <- read_html(url)
xpath <- "//h2[./span[@id='Anthropology']]/following-sibling::ul[1]/li"
html_nodes(url_parsed, xpath = xpath) %>% html_text()
```

<br>

*Python vs. R*

I often heard that using Python should be preferred over R for scraping tasks since Python is more versatile than R. Is that true?
 

<br> 

*Non-Latin scripts?* (etiennehoera)

I would like to scrape text in non-latin scripts (Chinese text specifically). Is there anything special I need to take care of? Matching seems to work using the same tools as in the examples.


## Dynamic scraping case study: querying IMDb
-------------------------------------------------

See 03-case-study-selenium.r


## Your questions on dynamic web scraping / Selenium
-------------------------------------------------------


**Some advice**

1. Have some version of Java installed. The latest SE version should work, but if you think that Java is an error source you might want to try other versions.

```{r}
system("java -version")
```

2. Get Selenium installed. The current implementation of the rsDriver() function automatically checks for current versions of the Selenium binary and associated drivers.

3. Trouble-shooting:
   - Selenium might require you to install the latest browser version (even if it's still beta!). If you can affort it, try it
   - Some browsers might not work at all, so you might want to switch browsers (Chrome + Firefox tend to be the most reliable options)
   - Add exception to firewall / antivirus software
   - Consult Stackoverflow




